(Working Title) Motor Vehicle Collisions Across Toronto

### 2024-01-19 outputs/paper/paper.qmd
updated title of paper

---
title: "(Working Title) Motor Vehicle Collision Across Toronto"
subtitle: "My subtitle if needed"
author: "Emily Su"
thanks: "Data and code are available at: https://github.com/moonsdust/toronto-collisions"
date: today
date-format: "D MMMM YYYY"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format:
  pdf:
    toc: true
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "(Working Title) Motor Vehicle Collisions Across Toronto"
subtitle: "My subtitle if needed"
author: "Emily Su"
thanks: "Data and code are available at: https://github.com/moonsdust/toronto-collisions"
date: today
date-format: "D MMMM YYYY"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format:
  pdf:
    toc: true
number-sections: true
bibliography: references.bib
---
